---
title: "Simulations for new features"
author: "Stefan"
date: "18. Dezember 2015"
output: html_document
---
This document contains the simulations conducted for the selected topic "TODO name".
You will find the following sections.
0. Load Package and reference runs
1. Random and Geographic Fission
2. Protracted Speciation
3. Red Queen Hypothesis / Boost 



0. Load Package
-----------------
First the package has to be loaded.
```{r}
library(PhyloSim)
```

Then I created a reference set of runs. This are five simulations under neutral conditions and point mutation.





1. Random fission
-----------------
Create the parameter sets:

```{r}
pars_fission<-list()
fission <-c(rep(1,5),rep(2,5))

for (i in 1:length(fission)){
  pars_fission[[i]] = createCompletePar(x = 50 ,y = 50, runs = 1000,
                                       dispersal = "global",
                                       specRate = 0.01,                                                                            density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=fission[i],
                                       redQueen = 0,
                                       redQueenStrength = 1)

}

```

Run the simulations:

```{r}

simu_fission <- runSimulationBatch(pars_fission) 

```


2. Protracted Speciation
------------------------
Create the parameter set:

```{r}
pars_protract<-list()
protract <-c(rep(1,5),rep(2,5))

for (i in 1:length(protract)){
  pars_protract[[i]] = createCompletePar(x = 50 ,y = 50, runs = 1000,
                                       dispersal = "global",
                                       specRate = 5,                                                                               density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       protracted = protract[i],
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 1)

}


```

Run the simulations:

```{r}

simu_protract <- runSimulationBatch(pars_protract) 

```


3. Red Queen
-------------------------
Create the parameter set:

```{r}
pars_redQueen<-list()
redQueen <-c(rep(0.1,5),rep(0.01,5))

for (i in 1:length(redQueen)){
  pars_redQueen[[i]] = createCompletePar(x = 50 ,y = 50, runs = 1000,
                                       dispersal = "global",
                                       specRate = 1,                                                                               density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       protracted = 0,
                                       fission=0,
                                       redQueen = redQueen[i],
                                       redQueenStrength = 2)

}


```

Run the simulations:

```{r}

simu_redQueen <- runSimulationBatch(pars_redQueen) 

```






You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
