---
title: "Simulations for new features"
author: "Stefan"
date: "08-01-2016"
output: html_document
---
This document contains the simulations conducted for the selected topic "Impact of Speciation Mechanisms on Ecological Patterns in Neutral and Quasi-Neutral Models".
You will find the following sections.
0. Load Package and reference runs 
1. Find comparable parameter values
2. Run the analysis


0. Load Package
-----------------
First the package has to be loaded.
```{r}
library(PhyloSim)
```


1. Find parameter values
---------------------
This section should give an impression about the strength of the effects of the different speciation mechanisms.
First I get a reference value under point mutation with a speciation rate of 1.

```{r}

parlist <- list()
parlistC <- list()

for(i in 1:10){
  parlist[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 1,                                                                                           density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0)
    parlistC[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 1,                                                                                           density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0)
  
  }



simu_test <- runSimulationBatch(parlist)

simu_testC <- runSimulationBatch(parlistC)


# Now get the values
specRichPoint <- numeric()
specRichPointC <- numeric()

for(i in 1:10){
  specRichPoint[i] <- specRich(simu_test[[i]])
  specRichPointC[i] <- specRich(simu_testC[[i]])
}
specRichPoint <- mean(specRichPoint)
specRichPointC <- mean(specRichPointC)
```

Then I compate this value to different speciation rates under fission.

```{r}

specRichF1 <- matrix(NA, 10,4)
specRichF2 <- matrix(NA, 10,4)

specRichF1C <- matrix(NA, 10,4)
specRichF2C <- matrix(NA, 10,4)

specRate <- c(0.005, 0.01, 0.05, 0.1)


for(k in 1:10){
parlistF1<- list()
parlistF2<- list()

parlistF1C<- list()
parlistF2C<- list()

for(i in 1:4){
  parlistF1[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = specRate[i],                                                                                 density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=1,
                                       redQueen = 0,
                                       redQueenStrength = 0)
  parlistF2[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = specRate[i],                                                                                 density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=2,
                                       redQueen = 0,
                                       redQueenStrength = 0)
  
    parlistF1C[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = specRate[i],                                                                                 density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=1,
                                       redQueen = 0,
                                       redQueenStrength = 0)
    
  parlistF2C[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = specRate[i],                                                                                 density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=2,
                                       redQueen = 0,
                                       redQueenStrength = 0)
}

simu_testF1 <- runSimulationBatch(parlistF1)
simu_testF2 <- runSimulationBatch(parlistF2)

simu_testF1C <- runSimulationBatch(parlistF1C)
simu_testF2C <- runSimulationBatch(parlistF2C)

# Now get the values

for(i in 1:4){
  specRichF1[k,i] <- specRich(simu_testF1[[i]])
  specRichF2[k,i] <- specRich(simu_testF2[[i]])
  
  specRichF1C[k,i] <- specRich(simu_testF1C[[i]])
  specRichF2C[k,i] <- specRich(simu_testF2C[[i]])
}
}


specRichF1m <- numeric()
specRichF2m <- numeric()

specRichF1mC <- numeric()
specRichF2mC <- numeric()

for(i in 1:4){
specRichF1m[i] <- mean(specRichF1[,i])
specRichF2m[i] <- mean(specRichF2[,i])

specRichF1mC[i] <- mean(specRichF1C[,i])
specRichF2mC[i] <- mean(specRichF2C[,i])
}


# And plot the results

par(mar=c(5, 4.5, 4, 4))
plot(specRate, specRichF1m, type="b", lwd=2, col="darkgreen",
     ylab="Species Richness", xlab="Speciation Rate", cex.axis=1.3, cex.lab=1.3, ylim=c(5,50))
abline(h=specRichPoint, lty=2)
lines(specRate, specRichF2m, lwd=2, type="b", col="darkblue")
legend(x=0.001, y=50, legend=c("Fission = 1", "Fission = 2"), lty=1, lwd=2,
       col=c("darkgreen","darkblue" ), bty="n")

plot(specRate, specRichF1mC, type="b", lwd=2, col="darkgreen",
     ylab="Species Richness", xlab="Speciation Rate", cex.axis=1.3, cex.lab=1.3)
abline(h=specRichPointC, lty=2)
lines(specRate, specRichF2mC, lwd=2, type="b", col="darkblue")
legend(x=0.001, y=45, legend=c("Fission = 1", "Fission = 2"), lty=1, lwd=2,
       col=c("darkgreen","darkblue" ), bty="n")

```

And under protracted speciation.

```{r}

sR5 <- sR10 <- matrix(NA, 10,4)
sR5C <- sR10C <- matrix(NA, 10,4)

for(k in 1:10){
  
pars5 <- list()
pars10 <- list()

pars5C <- list()
pars10C <- list()

for(i in 0:3){
 pars5[[i+1]] <-  createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 5,                                                                               density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       protracted = i,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0)

pars10[[i+1]] <-  createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 10,                                                                              density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       protracted = i,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0)

 pars5C[[i+1]] <-  createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 5,                                                                               density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       protracted = i,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0)

pars10C[[i+1]] <-  createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 10,                                                                              density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       protracted = i,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0)

}

simu_pars5 <- runSimulationBatch(pars5)
simu_pars10 <- runSimulationBatch(pars10)

simu_pars5C <- runSimulationBatch(pars5C)
simu_pars10C <- runSimulationBatch(pars10C)


for(i in 1:4){
  sR5[k,i]<-specRich(simu_pars5[[i]])
  sR10[k,i]<-specRich(simu_pars10[[i]])
  
  sR5C[k,i]<-specRich(simu_pars5C[[i]])
  sR10C[k,i]<-specRich(simu_pars10C[[i]])
}
}

sR5m <- numeric()
sR10m <- numeric()

sR5mC <- numeric()
sR10mC <- numeric()

for(i in 1:4){
  sR5m[i]<- mean(sR5[,i])
  sR10m[i]<-mean(sR10[,i])
  
  sR5mC[i]<- mean(sR5C[,i])
  sR10mC[i]<-mean(sR10C[,i])
}



# Plot the results
par(mar=c(5, 4.5, 4, 2))
plot(0:3, sR10m, type="b", ylim=c(0, max(sR10)), ylab="Species Richness",
     lwd=2, col="darkblue", xlab="Protracted", xaxt="n", cex.axis=1.3, cex.lab=1.3)

axis(side=1, at = c(0:3), cex.axis=1.3)
lines(0:3,sR5m, lwd=2, col="forestgreen", type="b")
abline(h=specRichPoint, lty=2)
legend(x=1.5,y=78, legend=c("SpecRate = 10", "SpecRate = 5"), lty=1,lwd=2, col=c("darkblue", "forestgreen"), bty="n")


plot(0:3, sR10mC, type="b", ylim=c(0, max(sR10C)), ylab="Species Richness",
     lwd=2, col="darkblue", xlab="Protracted", xaxt="n", cex.axis=1.3, cex.lab=1.3)

axis(side=1, at = c(0:3), cex.axis=1.3)
lines(0:3,sR5mC, lwd=2, col="forestgreen", type="b")
abline(h=specRichPointC, lty=2)
legend(x=1.5,y=78, legend=c("SpecRate = 10", "SpecRate = 5"), lty=1,lwd=2, col=c("darkblue", "forestgreen"), bty="n")

``` 

And under the Red Queen Mechanism.

```{r}

parsrQ <- list()
parsrQC <- list()



redQueen <- seq(0.01,1, len=10)
sRQ <- matrix(NA, 10,10)
sRQC <- matrix(NA, 10,10)

for(k in 1:10){
for(i in 1:10){
 parsrQ[[i]] <-  createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = redQueen[i],                                                                               density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       protracted = 0,
                                       fission=0,
                                       redQueen = 0.01,
                                       redQueenStrength = 2)
  parsrQC[[i]] <-  createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = redQueen[i],                                                                                  density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       protracted = 0,
                                       fission=0,
                                       redQueen = 0.01,
                                       redQueenStrength = 2)
}


simurQ <- runSimulationBatch(parsrQ)
simurQC <- runSimulationBatch(parsrQC)



for(i in 1:10){
  sRQ[k,i]<-specRich(simurQ[[i]])
  sRQC[k,i]<-specRich(simurQC[[i]])
}

}

srQmean <- numeric()
srQmeanC <- numeric()

for(i in 1:10){
  srQmean[i] <- mean(sRQ[,i])
  srQmeanC[i] <- mean(sRQC[,i])
}


## Plot the results
par(mar=c(5, 4.5, 4, 2))
plot(redQueen, srQmean, type="b", col="darkblue", lwd=2, xlab="Speciation Rate", 
    ylab="Species Richness", cex.axis=1.3, cex.lab=1.3)
abline(h=specRichPoint, lty=2)

plot(redQueen, srQmeanC, type="b", col="darkblue", lwd=2, xlab="Speciation Rate", 
    ylab="Species Richness", cex.axis=1.3, cex.lab=1.3)
abline(h=specRichPointC, lty=2)


```

2. Run the analysis
-----------------------
I use the best fitting parameter combinations from above and rerun the model for 10000 generations for each speciation mechanism.
First this is being done under the purely neutral model.
As above I have to run a reference model.

```{r}
par <- list()

for(i in 1:10){
par[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 1,                                                                                           density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0)
}
simu <- runSimulationBatch(par)

```

Than I can can run the model under the different speciation mechanisms.

```{r}

parF1 <- list()
parF2 <- list()
parP <- list()
parRQ <- list()

for(i in 1:10){
# Fissio type 1
parF1[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 0.01,                                                                                        density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=1,
                                       redQueen = 0,
                                       redQueenStrength = 0)



# Fissio type 2
parF2[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 0.01,                                                                                        density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=2,
                                       redQueen = 0,
                                       redQueenStrength = 0)



# Protracted Speciation
parP[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 5,                                                                                           density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0,
                                       protracted = 2)



# Red Queen
parRQ[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 0.6,                                                                                           density = 0,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0.01,
                                       redQueenStrength = 2,
                                       protracted = 0)

}

simuF1 <- runSimulationBatch(parF1)
simuF2 <- runSimulationBatch(parF2)
simuP <- runSimulationBatch(parP)
simuRQ <- runSimulationBatch(parRQ)

```

To get a first impression of the results:
```{r}
plot(simu)
plot(simuF1)
plot(simuF2)
plot(simuP)
plot(simuRQ)
```


The main focus of the analysis lies on the shape of the phylogenies.
Gamma statistics:

```{r}
library(ape)
gammaPoint <- gammaF1 <- gammaF2 <- gammaP <- gammaRQ <- numeric()

for(i in 1:10){
gammaPoint[[i]] <- gammaStat(drop.fossil(simu[[i]]$Output[[1]]$phylogeny))
gammaF1[[i]] <- gammaStat(drop.fossil(simuF1[[i]]$Output[[1]]$phylogeny))
gammaF2[[i]] <- gammaStat(drop.fossil(simuF2[[i]]$Output[[1]]$phylogeny))
gammaP[[i]] <- gammaStat(drop.fossil(simuP[[i]]$Output[[1]]$phylogeny))
gammaRQ[[i]] <- gammaStat(drop.fossil(simuRQ[[i]]$Output[[1]]$phylogeny))
}


barplot(c(mean(gammaPoint, na.rm = T), mean(gammaF1, na.rm = T), mean(gammaF2, na.rm = T), mean(gammaP, 
        na.rm = T), mean(gammaRQ, na.rm = T)),
        names.arg = c("Point", "F1", "F2", "Prot.", "RedQ"), col="lightslateblue",
        ylab="Gamma", cex.axis = 1.3, cex.lab=1.3, cex.names = 1.3)

data1 <- data.frame("Gamma"= c(gammaPoint, gammaF1, gammaF2, gammaP, gammaRQ), "SpecM"=
                      c(rep("Point",10),rep("F1",10),rep("F2",10),rep("Prot.",10),rep("RedQ",10)))

anova1 <- aov(Gamma~SpecM, data= data1)
summary(anova1)
boxplot(Gamma~SpecM, data=data1, col="lightsalmon", ylab="Gamma", xlab="Speciation Mechanism", cex.axis=1.3, cex.lab=1.3)

```


Colless Imbalance:

```{r}
library(phyloTop)
collessPoint <- collessF1 <- collessF2 <- collessP <- collessRQ <- rep(NA, 10)

for(i in 1:10){
collessPoint[i] <- colless(as(simu[[i]]$Output[[1]]$phylogeny, "phylo4"))
collessF1[i] <- colless(as(simuF1[[i]]$Output[[1]]$phylogeny, "phylo4"))
collessF2[i] <- colless(as(simuF2[[i]]$Output[[1]]$phylogeny, "phylo4"))
collessP[i] <- colless(as(simuP[[i]]$Output[[1]]$phylogeny, "phylo4"))
collessRQ[i] <- colless(as(simuRQ[[i]]$Output[[1]]$phylogeny, "phylo4"))
}

barplot(c(mean(collessPoint, na.rm = T), mean(collessF1, na.rm = T), mean(collessF2, na.rm = T),     
        mean(collessP, na.rm = T), mean(collessRQ, na.rm = T)),
        names.arg = c("Point", "F1", "F2", "Prot.", "RedQ"), col="lightslateblue",
        ylab="Colless' Imbalance", cex.axis = 1.3, cex.lab=1.3, cex.names = 1.3)


data2 <- data.frame("Colless"= c(collessPoint, collessF1, collessF2, collessP, collessRQ), "SpecM"=
                      c(rep("Point",10),rep("F1",10),rep("F2",10),rep("Prot.",10),rep("RedQ",10)))

anova2 <- aov(Colless~SpecM, data= data2)
summary(anova2)
Tukey2 <- TukeyHSD(anova2)

# Export to LaTeX
library(stargazer)
stargazer(Tukey2$SpecM)

boxplot(Colless~SpecM, data=data2, col="lightslateblue", ylab="Colless' Imbalance", xlab="Speciation Mechanism", cex.axis=1.3, cex.lab=1.3)

```

Now the same for non-neutral case. Here I chose density dependence.

```{r}
par <- list()

for(i in 1:10){
par[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 1,                                                                                           density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0)
}
simuC <- runSimulationBatch(par)

```

Than I can can run the model under the different speciation mechanisms.

```{r}

parF1 <- list()
parF2 <- list()
parP <- list()
parRQ <- list()

for(i in 1:10){
# Fissio type 1
parF1[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 0.01,                                                                                        density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=1,
                                       redQueen = 0,
                                       redQueenStrength = 0)



# Fissio type 2
parF2[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 0.01,                                                                                        density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=2,
                                       redQueen = 0,
                                       redQueenStrength = 0)



# Protracted Speciation
parP[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 5,                                                                                           density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0,
                                       protracted = 2)



# Red Queen
parRQ[[i]] <- createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = 0.6,                                                                                           density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0.01,
                                       redQueenStrength = 2,
                                       protracted = 0)

}

simuF1C <- runSimulationBatch(parF1)
simuF2C <- runSimulationBatch(parF2)
simuPC <- runSimulationBatch(parP)
simuRQC <- runSimulationBatch(parRQ)

```

To get a first impression of the results:
```{r}
plot(simuC)
plot(simuF1C)
plot(simuF2C)
plot(simuPC)
plot(simuRQC)
```


The main focus of the analysis lies on the shape of the phylogenies.
Gamma statistics:

```{r}
library(ape)
gammaPointC <- gammaF1C <- gammaF2C <- gammaPC <- gammaRQC <- numeric()

for(i in 1:10){
gammaPointC[[i]] <- gammaStat(drop.fossil(simuC[[i]]$Output[[1]]$phylogeny))
gammaF1C[[i]] <- gammaStat(drop.fossil(simuF1C[[i]]$Output[[1]]$phylogeny))
gammaF2C[[i]] <- gammaStat(drop.fossil(simuF2C[[i]]$Output[[1]]$phylogeny))
gammaPC[[i]] <- gammaStat(drop.fossil(simuPC[[i]]$Output[[1]]$phylogeny))
gammaRQC[[i]] <- gammaStat(drop.fossil(simuRQC[[i]]$Output[[1]]$phylogeny))
}


barplot(c(mean(gammaPointC), mean(gammaF1C), mean(gammaF2C), mean(gammaPC), mean(gammaRQC)),
        names.arg = c("Point", "F1", "F2", "Prot.", "RedQ"), col="lightslateblue",
        ylab="Gamma", cex.axis = 1.3, cex.lab=1.3, cex.names = 1.3)

data1C <- data.frame("Gamma"= c(gammaPointC, gammaF1C, gammaF2C, gammaPC, gammaRQC), "SpecM"=
                      c(rep("Point",10),rep("F1",10),rep("F2",10),rep("Prot.",10),rep("RedQ",10)))

anova1C <- aov(Gamma~SpecM, data= data1C)
summary(anova1C)

boxplot(Gamma~SpecM, data=data1C, col="lightsalmon", ylab="Gamma", xlab="Speciation Mechanism", cex.axis=1.3, cex.lab=1.3)

```


Colless Imbalance:

```{r}
library(phyloTop)
collessPointC <- collessF1C <- collessF2C <- collessPC <- collessRQC <- rep(NA, 10)

for(i in 1:10){
collessPointC[i] <- colless(as(simuC[[i]]$Output[[1]]$phylogeny, "phylo4"))
collessF1C[i] <- colless(as(simuF1C[[i]]$Output[[1]]$phylogeny, "phylo4"))
collessF2C[i] <- colless(as(simuF2C[[i]]$Output[[1]]$phylogeny, "phylo4"))
collessPC[i] <- colless(as(simuPC[[i]]$Output[[1]]$phylogeny, "phylo4"))
collessRQC[i] <- colless(as(simuRQC[[i]]$Output[[1]]$phylogeny, "phylo4"))
}

barplot(c(mean(collessPointC, na.rm = T), mean(collessF1C, na.rm = T), mean(collessF2C, na.rm = T),     
        mean(collessPC, na.rm = T), mean(collessRQC, na.rm = T)),
        names.arg = c("Point", "F1", "F2", "Prot.", "RedQ"), col="lightslateblue",
        ylab="Colless' Imbalance", cex.axis = 1.3, cex.lab=1.3, cex.names = 1.3)

data2C <- data.frame("Colless"= c(collessPointC, collessF1C, collessF2C, collessPC, collessRQC), "SpecM"=c(rep("Point",10),rep("F1",10),rep("F2",10),rep("Prot.",10),rep("RedQ",10)))

anova2C <- aov(Colless~SpecM, data= data2C)
summary(anova2C)

Tukey2C<-TukeyHSD(anova2C)

# Export to LaTeX
library(stargazer)
stargazer(Tukey2C$SpecM)

boxplot(Colless~SpecM, data=data2C, col="lightslateblue", ylab="Colless' Imbalance", xlab="Speciation Mechanism", cex.axis=1.3, cex.lab=1.3)


# Both in one plot
par(mfrow=c(1,2))
par(mar=c(5, 4.1, 4, 0.1))

boxplot(Colless~SpecM, data=data2, col="lightslateblue", ylab="Colless' Imbalance", xlab="Speciation Mechanism", cex.axis=1.05, cex.lab=1.2, main="Neutral")

par(mar=c(5, 2.8, 4, 1.5))

boxplot(Colless~SpecM, data=data2C, col="lightslateblue", ylab="", xlab="Speciation Mechanism", cex.axis=1.05, cex.lab=1.2, main="Competition")



```


Finally I wanted to see if the speciation rate influences the Gamma Statistics in a neutral model. This helps me to interprete the results of the simulations above.


```{r}

require(ape)
specRatet <- seq(1,5, len=10)

gammat <- matrix(NA, 10,10)

for(k in 1:5){
  paramt <- list()
for(i in 1:10){
  paramt[[i]] <-createCompletePar(x = 50 ,y = 50, runs = 10000,
                                       dispersal = "global",
                                       specRate = specRatet[i],                                                                       density = 1,
                                       environment = 0,
                                       fitnessBaseMortalityRatio = 5,
                                       densityCut = 1,
                                       fission=0,
                                       redQueen = 0,
                                       redQueenStrength = 0,
                                       protracted = 0)

}

simut <- runSimulationBatch(paramt)
for(i in 1:10){
    gammat[k,i] <- gammaStat(drop.fossil(simut[[i]]$Output[[1]]$phylogeny))

}
}

gammatm <- numeric()
for(i in 1:10){
  gammatm[i] <- mean(gammat[,i], na.rm=T)
}


par(mar=c(5, 4.5, 4, 2))
plot(specRatet, gammatm, type="b", col="darkblue", lwd=2, ylab="Gamma",
     xlab="Speciation Rate", cex.lab=1.3, cex.axis=1.3)

```