---
title: "Run Simulations"
author: "Stefan"
date: "4. Dezember 2015"
output: pdf_document
---

This document describes the experimental design that has been used to assess the model output.
You'll find the following steps:
- 1. Loading the package
- 2. Defining the parameter sets
- 3. Running the simulations

1. Loading the package
--------------------------------
```{r}
library(PhyloSim)
```

2. Defining the parameter sets
------------------------------
We will run two different sets of simualtions. The first set will be run on a grid of 100*100 cells for 100.000 generations. The second set will be run on a grid of 256*256 for 500.000 generations.
Except for these parameters the setup will be identical.
We conduct 28 simulations consisting of seven combinations of the parameters 'density' and 'environment' wich will be simulated for four different dispersal distances.
To control wheter the results are stable ten different time steps will be saved.

```{r}
 setwd("C:/Users/Stefan/Desktop/PhyloSim_Simulations/100000runs")
runs100 = seq(50000,100000, len=10)
runs256 = seq(100000,500000, len=10)

dispOptions = 4
fitOptions = 7

dispersal =  rep(c(0,0.5, 2,4), each = fitOptions)
density = rep(c(0,seq(0,1,len = fitOptions-2),1),dispOptions)
environment = rep(c(0,seq(1,0,len = fitOptions-2),1),dispOptions)

modes <- ifelse(dispersal == 0, "global", "local")
scenarios <- paste(modes, " dens=", density, " env=", environment, sep = "")

pars100 <- list()
pars256 <- list()


for (i in 1:length(scenarios)){pars100[[i]] = createCompletePar(x = 100 ,y = 100, runs = runs100,
                                                             scenario = scenarios[i],
                                                             dispersal = dispersal[i],
                                                             specRate = 1,
                                                             density = density[i],
                                                             environment = environment[i],
                                                             fitnessBaseMortalityRatio = 5,
                                                             densityCut = 1, seed = 1000)
                                pars256[[i]] = createCompletePar(x = 256 ,y = 256, runs = runs256,
                                                             scenario = scenarios[i],
                                                             dispersal = dispersal[i],
                                                             specRate = 1,
                                                             density = density[i],
                                                             environment = environment[i],
                                                             fitnessBaseMortalityRatio = 5,
                                                             densityCut = 1, seed = 1000)

}
```

3. Running the simulations
------------------------
```{r}
system.time(simulationOut100 <- runSimulationBatch(pars100, parallel = 15))
save(simulationOut, pars, file = "results100x100.Rdata" )

system.time(simulationOut256 <- runSimulationBatch(pars256, parallel = 15))
save(simulationOut, pars, file = "results256x256.Rdata" )

```