---
title: "Null Models Test"
author: "Stefan"
date: "25. November 2015"
output: html_document
---
This document describes the which simulations have been conducted and how they have been analyzed.
You'll find the following steps:

- 4. Phylogenetic Dispersion (Null Models)
- 5. Species Richness
- 6. Gamma Statistics
- 7. Colless' Imbalance


4. Calculation of the null models
-----------------------------------

```{r}
load("results100x100.Rdata")
nullMeta100 <- calculatePhylogeneticDispersion(simulationOut100, plotlengths = c(2,3,4,5,6,7,8,9,10))
save(nullMeta, file="nullmeta100x100.RData")

load("results256x256.Rdata")
nullMeta256 <- calculatePhylogeneticDispersion(simulationOut256, plotlengths = c(2,3,4,5,6,7,8,9,10))
save(nullMeta, file="nullmeta256x256.RData")

```

5. Species Richness
----------------------------------------------
The species richness is calculated for every recorded timestep.
The results are stored in two matrices.
```{r}
SpeciesRichness100 <- matrix(NA, 28, 10)
SpeciesRichness256 <- matrix(NA, 28, 10)

for(i in 1:28){
    for(k in 1:10){
      SpeciesRichness100[i,k] <- specRich(simulationOut100[[i]], which.result = k)
      SpeciesRichness256[i,k] <- specRich(simulationOut256[[i]], which.result = k)
    }
}

save(SpeciesRichness100, file = "SpecRich100x100.RData")
save(SpeciesRichness256, file = "SpecRich256x256.RData")
```

6. Gamma Statistics
--------------------------------
Note: We use phylogenetic indeices as a measure of rubustness of our results but we do not know if these values remain constant over time in an equilibrium state of the model. Hence, we only expect that there is no trend in our data over time if the model is in an equilibrium state.

The Gamma statistic is a measure of the relative positions of internal nodes
within a phylogeny. If \gamma < 0 then the internal nodes are closer to the root than
expected under a pure-birth model. If \gamma > 0 the nodes are closer to the tips.
The Gamma statistic is calculated for every recorded time step.



The test we use is part of the 'ape' package. 

```{r}
library(ape)
```



```{r}
gammas100 <- matrix(NA, 28, 10)
gammas256 <- matrix(NA, 28, 10)

for(i in 1:28){
  for(k in 1:10){
    extant100 <- drop.fossil(simulationOut100[[i]]$Output[[k]]$phylogeny)
    gammas100[i, k]<-gammaStat(extant100)

    extant256 <- drop.fossil(simulationOut256[[i]]$Output[[k]]$phylogeny)
    gammas256[i, k]<-gammaStat(extant256)        
  }
}

save(gammas100, file="GammaStat100.RData")
save(gammas256, file="GammaStat256.RData")

```


7. Colless' Imbalance
------------------------------------

Second we look at the balance of a tree. This is the degree to which sister clades tend to be of equal size (Rogers, 1994).
We use Colless Imbalance as a measure for the (im)balance of the tree. It is defined as the sum of all the node imbalances divided by 2/((n-1)(n-2)) where n is the number of tips.
The Imbalance is calculated for every recorded time step. If the tree is not rooted and fully dichotomous the function returns an 'NA' value.  

```{r}
colless100 <- matrix(NA, 28, 10)
colless256 <- matrix(NA, 28, 10)

for(i in 1:28){
  for(k in 1:10){
    colless100[i,k] <- collessImbalance(simulationOut100[[i]], which.result=k)
    colless256[i,k] <- collessImbalance(simulationOut256[[i]], which.result=k)   
  }
}

save(colless100, file="Colless100.RData")
save(colless256, file="Colless256.RData")

```


