---
title: "Null Models Test"
author: "Stefan"
date: "25. November 2015"
output: html_document
---
This document describes the which simulations have been conducted and how they have been analyzed.
You'll find the following steps:
- Loading the package
- Defining the parameter sets
- Running the simulations
- Calculation of the null models
- Plotting the results

Loading the package
--------------------------------


```{r}
library(PhyloSim)
```

Defining the parameter sets
------------------------------
The simulation will run on a grid of 100*100 cells for 10000 generations.
In this setup there will be 28 simulations. They consist of seven combinations of the parameters 'density' and 'environment' wich will be simulated for four different dispersal distances.
To control wheter the results are stable the results are recorded every 1000 generations.

```{r}
setwd("C:/Users/Stefan/Desktop/PhyloSim_Simulations")
# runs = seq(5000,10000, len=10)
# 
# dispOptions = 4
# fitOptions = 7
# 
# dispersal =  rep(c(0,0.5, 2,4), each = fitOptions)
# density = rep(c(0,seq(0,1,len = fitOptions-2),1),dispOptions)
# environment = rep(c(0,seq(1,0,len = fitOptions-2),1),dispOptions)
# 
# modes <- ifelse(dispersal == 0, "global", "local")
# scenarios <- paste(modes, " dens=", density, " env=", environment, sep = "")
# 
# pars <- list()
# 
# for (i in 1:length(scenarios)){pars[[i]] = createCompletePar(x = 100 ,y = 100, runs = runs,
#                                                              scenario = = scenarios[i],
#                                                              dispersal = dispersal[i],
#                                                              specRate = 1,
#                                                              density = density[i],
#                                                              environment = environment[i],
#                                                              fitnessBaseMortalityRatio = 5,
#                                                              densityCut = 1, seed = 1000)}
```

Running the simulations
------------------------
```{r}
# system.time(simulationOut <- runSimulationBatch(pars, parallel = "auto"))
# 
# save(simulationOut, pars, file = "results100x100.Rdata" )
```

Calculation of the null models
-----------------------------------

```{r}
# load("results100x100.Rdata")
# 
# nullMeta <- calculatePhylogeneticDispersion(simulationOut,plotlengths = c(2,3,4,5,6,7,8,9,10))
# 
# save(nullMeta, file="nullmeta100x100.RData")
```

Plotting the results
-------------------------

```{r}
load("nullmeta100x100.RData")
 
positions <- list(x= c(1:7),
    y = c(4, 1:3), # this is beacause dispersal = "global" is equal to dispersal = "0"
    xname = c("neutral", "1", "0.75", "0.5", "0.25", "0", "both"), # = environment
    yname = c("global", "0.5", "2", "4"),  # = dispersal
    zname=c("neutral", "0", "0.25", "0.5","0.75","1","both")) # = density
 

plotPhylogeneticDispersion(pvalues = nullMeta, positions = positions,  title = "Null Meta")

plotPhylogeneticDispersion(pvalues = nullMeta, positions = positions, which.simualtion = 1,  title = "Null Meta")

plotPhylogeneticDispersion(pvalues = nullMeta, positions = positions, which.simualtion = 2,  title = "Null Meta")


```






