---
title: "Null Models Test"
author: "Stefan"
date: "25. November 2015"
output: html_document
---
This document describes the which simulations have been conducted and how they have been analyzed.
You'll find the following steps:
- Loading the package
- Defining the parameter sets
- Running the simulations
- Calculation of the null models
- Plotting the results
- Phylogenetic indices

Loading the package
--------------------------------


```{r}
library(PhyloSim)
```

Defining the parameter sets
------------------------------
The simulation will run on a grid of 100*100 cells for 10000 generations.
In this setup there will be 28 simulations. They consist of seven combinations of the parameters 'density' and 'environment' wich will be simulated for four different dispersal distances.
To control wheter the results are stable the results are recorded every 1000 generations.

```{r}
setwd("C:/Users/Stefan/Desktop/PhyloSim_Simulations")
# runs = seq(5000,10000, len=10)
# 
# dispOptions = 4
# fitOptions = 7
# 
# dispersal =  rep(c(0,0.5, 2,4), each = fitOptions)
# density = rep(c(0,seq(0,1,len = fitOptions-2),1),dispOptions)
# environment = rep(c(0,seq(1,0,len = fitOptions-2),1),dispOptions)
# 
# modes <- ifelse(dispersal == 0, "global", "local")
# scenarios <- paste(modes, " dens=", density, " env=", environment, sep = "")
# 
# pars <- list()
# 
# for (i in 1:length(scenarios)){pars[[i]] = createCompletePar(x = 100 ,y = 100, runs = runs,
#                                                              scenario = scenarios[i],
#                                                              dispersal = dispersal[i],
#                                                              specRate = 1,
#                                                              density = density[i],
#                                                              environment = environment[i],
#                                                              fitnessBaseMortalityRatio = 5,
#                                                              densityCut = 1, seed = 1000)}
```

Running the simulations
------------------------
```{r}
# system.time(simulationOut <- runSimulationBatch(pars, parallel = "auto"))
# 
# save(simulationOut, pars, file = "results100x100.Rdata" )
```

Calculation of the null models
-----------------------------------

```{r}
# load("results100x100.Rdata")
# 
# nullMeta <- calculatePhylogeneticDispersion(simulationOut,plotlengths = c(2,3,4,5,6,7,8,9,10))
# 
# save(nullMeta, file="nullmeta100x100.RData")
```

Plotting the results
-------------------------

```{r}
load("nullmeta100x100.RData")
 
positions <- list(x= c(1:7),
    y = c(4, 1:3), # this is beacause dispersal = "global" is equal to dispersal = "0"
    zname = c("neutral", "1", "0.75", "0.5", "0.25", "0", "both"), # = environment
    yname = c("global", "0.5", "2", "4"),  # = dispersal
    xname=c("neutral", "0", "0.25", "0.5","0.75","1","both")) # = density
 

plotPhylogeneticDispersion(pvalues = nullMeta, positions = positions,  title = "Null Meta")

plotPhylogeneticDispersion(pvalues = nullMeta, positions = positions, which.simualtion = 1,  title = "Null Meta")

plotPhylogeneticDispersion(pvalues = nullMeta, positions = positions, which.simualtion = 2,  title = "Null Meta")


```

Phylogenetic indices
--------------------------------
Note: By using phylogenetic indices as a measure of robustness of ur results,
we assume that these values remain constant over time for a metacommunity in equilibrium.
However, we do not know if that realy is the case....

The first test computes the gamma statistics of the phylogeny tree.
The test is part of the 'ape' package. 

```{r}
library(ape)
```

It assumes that the tree is ultrametric. If not, the results may not be useful.
This can be tested as follows.

```{r}
extant<-drop.fossil(simulationOut[[1]]$Output[[10]]$phylogeny)
is.ultrametric(extant, tol = .Machine$double.eps^0.5)
```

If this precondition is fulfilled, the gamma statistics for a certain tree can be
calculated. This statistic is a measure of the relative positions of internal nodes
within a phylogeny. If \gamma < 0 then the internal nodes are closer to the root than
expected under a pure-birth model. If \gamma > 0 the nodes are closer to the tips.
Here we calculate the gamma statistics for the 10 results saved
for the first scenario.

```{r}

library(ape)
gammas<-numeric()


for(i in 1:10){
  extant<-drop.fossil(simulationOut[[1]]$Output[[i]]$phylogeny)
  gammas[i]<-gammaStat(extant)
}

plot(seq(5000,10000,len=10),gammas, type="b")
```
Second we look at the balance of a tree. This is the degree to which sister clades tend to be of equal size (Rogers, 1994).
We use Colless Imbalance as a measure for the (im)balance of the tree. It is defined as the sum of all the node imbalances divided by 2/((n-1)(n-2)) where n is the number of tips.
The function used here orinigns in the 'phyloTop' package. 
As above the test is exemplarily shown for all recorded results of the first scenario.

```{r}
library(phyloTop)

coll<-numeric()
for(i in 1:10){
    extant<-drop.fossil(simulationOut[[1]]$Output[[i]]$phylogeny)
coll[i]<-colless(as(extant, "phylo4"))
}

plot(seq(5000,10000,len=10),coll, type="b")
```



