---
title: "Spatial Plots"
author: "Florian Hartig"
date: "27 Aug 2015"
output: html_document
---

```{r}
require(PhylGeo)
require(ape)
require(picante)
library(shape)
library(spam)
library(fields)
load("../results/results100x100.Rdata" )

outfolder = "plots100"

dir.create(paste("./",outfolder, sep = ""))
```


# Calculating p-values from null models 
This first impression leads to the assumption, that there is some signal in the phylogenetic dispersion which might help us identify environmental filtering or competitive exclusion as mechanisms. To quantify the degree of dispersion we compare our observed data against a null model. This null model can be calculated from the metacommunity or from samples.  


```{r, cache=T}

nullMeta <- calculatePhylogeneticDispersion(simulationOut, plotlengths = c(2,3,4,5,6,7,8,9,10), reduce = T)
```

```{r, cache=T}

nullSample <- calculatePhylogeneticDispersion(simulationOut, type = "PhylSample", plotlengths = c(2,3,4,5,6,7,8,9,10), reduce = T)
```

```{r, cache=T}

samplePool <- calculatePhylogeneticDispersion(simulationOut, type = "SamplePool", plotlengths = c(2,3,4,5,6,7,8,9,10), reduce = T)
```

```{r, cache=T}

phylPool <- calculatePhylogeneticDispersion(simulationOut, type = "PhylPool", plotlengths = c(2,3,4,5,6,7,8,9,10), reduce = T)
```


```{r}

positions <- list(x= c(1, seq(2.5,6.5,1), 8),
                   y = c(4, 1:3),
                   xname = c("neutral", "1", "0.75", "0.5", "0.25", "0", "both"),
                   yname = c("global", "0.5", "2", "4" ))

```




```{r}
save.image( file = "NullModelResults.RData")

plotPhylogeneticDispersion(nullMeta, positions, "Null Meta", multiple = T) 

name =   name <- paste("./",outfolder, "/NullMeta.pdf", sep = "")

dev.copy(pdf, name , width=8, height=6)
dev.off()

plotPhylogeneticDispersion(nullSample, positions, "Null Sample", multiple = T) 

dev.copy(pdf,"./plots/NullSample.pdf", width=8, height=8)
dev.off()

plotPhylogeneticDispersion(samplePool, positions, "Null Sample Pool (picante)", multiple = T) 

dev.copy(pdf,"./plots/NullPicanteSample.pdf", width=8, height=8)
dev.off()

plotPhylogeneticDispersion(phylPool, positions, "Null Phyl Pool (picante)", multiple = T) 

dev.copy(pdf,"./plots/NullPicantePhylo.pdf", width=8, height=8)
dev.off()
```



##### The following code is only useful if your simulationOut object is
## in the old format.
#### Adaptions to the new format
######################################

##load the data
load("results100x100-2.RData")

## Make data compatible to new format
## speed the process only the last time step is transferred (can easily be changed to all)

output<-list()
output[[1]]<-list("Output"=list(simulationOut[[1]][[50]]),"Model"=simulationOut[[1]][[51]])
class(output[[1]])<-c(class(output),"Phylosim")

for(i in 2:28){
  outputnew<-list("Output"=list(simulationOut[[i]][[50]]),"Model"=simulationOut[[i]][[51]])
  output[[i]]<-outputnew
  class(output[[i]])<-c(class(outputnew),"Phylosim")
}




### Do the calculations

nullMeta <- calculatePhylogeneticDispersion(output, plotlengths = c(2,3,4,5,6,7,8,9,10), reduce = T)

nullSample <- calculatePhylogeneticDispersion(output, type = "PhylSample", plotlengths = c(2,3,4,5,6,7,8,9,10), reduce = T)

samplePool <- calculatePhylogeneticDispersion(output, type = "SamplePool", plotlengths = c(2,3,4,5,6,7,8,9,10), reduce = T)

phylPool <- calculatePhylogeneticDispersion(output, type = "PhylPool", plotlengths = c(2,3,4,5,6,7,8,9,10), reduce = T)
```


## Plot the results
positions <- list(x= c(1, seq(2.5,6.5,1), 8),
                  y = c(4, 1:3),
                  xname = c("neutral", "1", "0.75", "0.5", "0.25", "0", "both"),
                  yname = c("global", "0.5", "2", "4" ))

plotPhylogeneticDispersion(nullMeta, positions, "Null Meta", multiple = T)


