---
title: "equilibriumCheck"
output: 
  html_document:
    keep_md: true
---

This is the analysis of 100 simulation runs. 
These runs where conducted with a grid size of 50 by 50 cells. 
Each simulation was run over 100k generations with the same settings. 
The only thing different in each run was the random seed. 
This analysis is designed to assess the variation between simulation runs and to determine whether the model reaches equilibrium. 

```{r packages_and_data}
require(PhylGeo)
require(shape)
require(fields)
require(vegan)


#loading the data
files = character()
for (i in 1:100){
files[i] = paste("local1_", i, collapse = "", sep = "")
}
localList <- list()
for(i in 1:length(files)){
  file <- paste("C:/Users/Paul/Desktop/Data/",files[i], ".rdata", collapse="", sep="")
  load(file)
  localList[[i]] <- OUT
  
}
names(localList) <- files
rm(file, files, i, OUT)
``` 

```{r calculating_pValues}
pvals <- list()
for(i in 1:length(localList)){
  print(i)
  s <- matrix(localList[[1]]$specOut, nrow = 50, ncol = 50)
  phyl <- read.tree(text = localList[[1]]$phyloOut)
  extantPhylo <- drop.fossil(phy = phyl)
  phy.exta <- cophenetic(extantPhylo)
  set.seed(1500)
  comMat <- localPlots(size = 25, n = 100,matrix = s, community = T)$communityTable
  set.seed(Sys.time())
  SES.mntd.phylogeny.pool <- ses.mpd(comMat, phy.exta, "phylogeny.pool",runs=999)  #4
  # SES.mntd.phylogeny.pool <- ses.pd(comMat, extantPhylo, "richness",runs=999, iterations=1000, include.root = TRUE)  #4
  pvals[[i]] <- SES.mntd.phylogeny.pool
}

names(pvals) <- names(localList)
```

```{r summarizing_pValues}
# colPal <- colorRampPalette(c('blue','white','red'))
z <- numeric()
zSD <- numeric()
for(i in 1:length(pvals)){
  z[i] <- mean(pvals[[i]]$mpd.obs.p, na.rm = T)
  zSD[i] <- sd(pvals[[i]]$mpd.obs.p, na.rm = T)
}
# Cols <- colPal(length(z))[rank(z)]
pValues <- data.frame(Scenario = names(pvals), disp_Dist = rep(1,10), meanPval = z, sdPval = zSD)


```

## Dispersion Patterns
```{r display_phylogenetic_patterns, echo=FALSE, fig.width=8, fig.height=8}
# par(mar=c(5.1, 4.1, 4.1, 9.1), xpd=TRUE)
mp <- barplot(z, axes=TRUE, axisnames=FALSE, ylim=c(0.0, 1.0),col=rainbow(length(localList)), main="pValues SES", xlab="Dispersal Distance", ylab="SES pValue", names.arg=(names(pvals)))
segments(mp, z - zSD, mp, z + zSD, lwd=2)
# Now plot the horizontal bounds for the error bars
# 1. The lower bar
segments(mp - 0.1, z - zSD, mp + 0.1, z - zSD, lwd=2)
# 2. The upper bar
segments(mp - 0.1, z + zSD, mp + 0.1, z + zSD, lwd=2)
# legend(legend= names(localList),"topright",  fill = rainbow(length(localList)), bty = "n")
par(mar=c(2, 2, 2, 2), xpd=FALSE)
```

## Species Richness 

The species richness was calculated twice. Once with all species found in the metacommunity and once with all species which had an abundance of at least 10 individuals to correct for nearly extinct or recently emerged species.

```{r calculating_and_plotting_species_richness, fig.width=8, fig.height=8}
a <- l <- numeric()
for(i in 1:length(localList)){
  s <- matrix(localList[[i]]$specOut, nrow = 50, ncol = 50)
  a[i] <- length(table(s))
  l[i] <- length(table(s)[which(table(s)>=10)])
}
par(mfrow=c(2,1))
# par(mar=c(5.1, 4.1, 4.1, 9.1), xpd=TRUE)
barplot(a, col = rainbow(length(localList)), ylab = "Species Richness", main = "SR", xlab="Scenarios")
abline(h = es(specRate = 2, dimensions = 50), lwd = 4)
abline(h = mean(a), lwd = 2)
abline(h = mean(a) + sd(a), lty=2, lwd = 2)
abline(h = mean(a) - sd(a), lty=2, lwd = 2)
# legend(legend= names(localList),"right",  fill = rainbow(length(localList)), bty = "n")
par(mar=rep(3,4), xpd=F)


# par(mar=c(5.1, 4.1, 4.1, 9.1), xpd=TRUE)
barplot(l, col = rainbow(length(localList)), ylab = "Species Richness", main = "SR", xlab="Scenarios")
abline(h = es(specRate = 2, dimensions = 50), lwd = 4)
abline(h = mean(l), lwd = 2)
abline(h = mean(l) + sd(l), lty=2, lwd = 2)
abline(h = mean(l) - sd(l), lty=2, lwd = 2)
# legend(legend= names(localList),"right",  fill = rainbow(length(localList)), bty = "n")
par(mar=rep(3,4), xpd=F)

hist(a, breaks = 25)
x<-seq(14,40,length=25)
y<-dnorm(x,mean=mean(a), sd=sd(a))
lines(x,y*100, type="l", lwd=2)


hist(l, breaks = 25)
x<-seq(9,27,length=25)
y<-dnorm(x,mean=mean(l), sd=sd(l))
lines(x,y*100, type="l", lwd=2)
par(mfrow=c(1,1))
```

```{r plotting_the_species_landscape, fig.width=10, fig.height=10}
par(mfrow=c(10,10), xpd=F, mar=c(2,2,2,2))
for(i in 1:length(localList)){
  s <- matrix(localList[[i]]$specOut, nrow = 50, ncol = 50)
  image(s, col = rainbow(length(table(s))), main = names(localList)[i])
}
par(mfrow=c(1,1))
```

```{r plotting_RACs, fig.width=8, fig.height=8}
colo <- rainbow(length(localList))
plot(rac(s, plot=F), xlim=c(0,40), log="y", type="l", col=colo[1], main = "RAC", lwd = 2, ylim=c(1,2500))
for(i in 2:length(localList)){
  s <- matrix(localList[[i]]$specOut, nrow = 50, ncol = 50)
  lines(rac(s, plot = F), col=colo[i], lwd = 2)
}
legend(legend= names(localList),"topright",  fill = rainbow(length(localList)), bty = "n")
```

```{r calculating_diversity_indices}
communityTable <- data.frame(species = numeric())
for(i in 1:length(localList)){
s <- matrix(localList[[i]]$specOut, nrow = 50, ncol = 50)
dataTable <- as.data.frame(table(s))
names(dataTable) <- c("species", paste("metacommunity", i, collapse="", sep="")) 
communityTable <- merge(communityTable, dataTable , all=T)
communityTable[is.na(communityTable)] <- 0
}

speciesNames <- character()
for(b in 1:length(communityTable$species)){
  speciesNames[b] <-  paste("s" ,communityTable$species[b], collapse="", sep="")
}
  communityTable$species <- speciesNames
  communityTable <- as.data.frame(t(communityTable), stringsAsFactors=F)
  communityTable <- communityTable[-1,]
  names(communityTable) <- speciesNames
  communityTable <- as.data.frame(sapply(communityTable, as.numeric), row.names=row.names(communityTable))
  ```